Retrofitting Effect Handlers onto OCaml

### 2020-11-17 retro-concurrency.tex
edits

In this section, we present the implementation details of effect handlers in
Multicore OCaml. Multicore OCaml currently only supports the x86-64 backend on
Linux, but our design does not preclude other backends. We assume x86-64
architecture in the sequel.

>>>>

We now present the implementation details of effect handlers in
Multicore OCaml. We assume an x86\_64 architecture for the remainder of this paper
-- although  Multicore OCaml currently only supports the x86\_64 backend on
Linux, our design is intended to support other CPUs and OSs.
